New lower bounds for Schur and weak Schur numbers

### 2021-05-04 article/introduction.tex

\renewcommand{\arraystretch}{1.2}
\setlength{\tabcolsep}{4pt}

@@

\begin{tabular}{|*{13}{c|}}
    \hline
    \(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
    \hline
    \multirow{2}{*}{before Rowley} & 1* & 4* & 13* & 44* & 160* & 536 & 1680 & 5041 & 15124 & 51120 & 172216 & 575664 \\
      & & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{ELIAHOU2012175} & 
    \cite{ELIAHOU2012175} & \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
    \hline
    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyRamsey}\end{tabular} & & & & & & & & 5286 & 17694 & 
    60320 & 201696 & 631840 \\
    \hline
    \hyperref[Schur]{our results}  & & & & & & & & & \textbf{17803} & \textbf{60948} & \textbf{203828} & \textbf{638548} \\
    \hline
\end{tabular}
*these values are not just a lower bound but the exact value for S(n)
\vspace{3ex}
\setlength{\tabcolsep}{4pt}

@@

\begin{tabular}{|*{13}{c|}}
    \hline
    \(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
    \hline
    \multirow{2}{*}{before Rowley} & 2* & 8* & 23* & 66* & 196 & 582 & 1740 & 5201 & 15596 & 51520 & 172216 & 575664 \\
      & & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
    \cite{Rafilipojaona} & \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
    \hline
    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyWS}\end{tabular} & & & & & & 642 & 2146 & 6976 & 21848 
    & 70778 & 241282 & 806786 \\
    \hline
    \hyperref[WeakSchur]{our results} & & & & & & & & & \textbf{22536} & \textbf{71214} & \textbf{243794} & \textbf{815314} \\
    \hline
\end{tabular}
*these values are not just a lower bound but the exact value for WS(n)
\end{center}

>>>>

\setlength{\tabcolsep}{4pt}

@@

\begin{tabular}{|*{13}{c|}}
    \hline
    \(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
    \hline
    \multirow{2}{*}{before Rowley} & 1* & 4* & 13* & 44* & 160* & 536 & 1\,680 & 5\,041 & 15\,124 & 51\,120 & 172\,216 & 575\,664 \\
      & & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{ELIAHOU2012175} & 
    \cite{ELIAHOU2012175} & \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
    \hline
    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyRamsey}\end{tabular} & & & & & & & & 5\,286 & 17\,694 & 
    60\,320 & 201\,696 & 631\,840 \\
    \hline
    \hyperref[Schur]{\textbf{our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{638\,548} \\
    \hline
\end{tabular}

\vspace{2.5ex}

@@

\begin{tabular}{|*{13}{c|}}
    \hline
    \(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
    \hline
    \multirow{2}{*}{before Rowley} & 2* & 8* & 23* & 66* & 196 & 582 & 1\,740 & 5\,201 & 15\,596 & 51\,520 & 172\,216 & 575\,664 \\
      & & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
    \cite{Rafilipojaona} & \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
    \hline
    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyWS}\end{tabular} & & & & & & 642 & 2\,146 & 6\,976 & 21\,848 
    & 70\,778 & 241\,282 & 806\,786 \\
    \hline
    \hyperref[WeakSchur]{\textbf{our results}} & & & & & & & & & \textbf{22\,536} & \textbf{71\,214} & \textbf{243\,794} & \textbf{815\,314} \\
    \hline
\end{tabular}

\vspace{1.5ex}
* denotes an exact value, not just a lower bound
\end{center}

### 2021-05-04 article/weakschur.tex
Changement de titres

\section{Weak Schur numbers}
\label{WeakSchur}

@@

\subsection{Lower bound for Weak Schur numbers using Schur and Weak Schur numbers}

@@

\renewcommand{\arraystretch}{2}
\[
\begin{array}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
\cline{6-9}
   \multicolumn{5}{c|}{} & \cellcolor{green} 1 & \cellcolor{green} 2 & \cellcolor{blue} ... &\cellcolor{green} r & r + 1 & ... & b - 1 &  b \\
\hline
   \cellcolor{red} a - l & \cellcolor{red} a- l + 1 & \cellcolor{red} ... & \cellcolor{red} a - 1 & \cellcolor{red} a & \cellcolor{red} a + 1 & \cellcolor{red} ... &\cellcolor{red} a + r - 1 & \cellcolor{red} a + r & a + r + 1 & ... & a + b - 1 & a+ b \\
\hline
\cellcolor{yellow} 2 a - l &\cellcolor{yellow}...&\cellcolor{yellow}...&\cellcolor{yellow}...&\cellcolor{yellow} 2 a &\cellcolor{yellow} ... &\cellcolor{yellow} ... &\cellcolor{yellow} ... &\cellcolor{yellow} 2 a + r & ... & ... & ... & 2 a + b \\
\hline
...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
\hline
\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
\hline
p a - l & ... & ... & ... &p a & ... & ... & .... & p a + r & ... & ... & ... & p a + b\\
\hline
\end{array}
\]
\renewcommand{\arraystretch}{1}

@@

\(\lambda\) is the function which maps an element x to its line number as mentioned in the intuitive explanation.

@@

\subsection{New lower bounds for Weak Schur numbers}

@@

\begin{center}
\begin{tabular}{|*{5}{c|}}
    \hline
	n & 8 & 9 & 10 & 11 \\
	\hline
	\(4S(n-1) + 2 \) & 6722 & 21146 & \cellcolor{yellow} 71214 & \cellcolor{yellow} 243794\\
	\hline
	\(13S(n-2) + 8 \) & \cellcolor{yellow} 6976 & 21848 & 68726 & 231447\\
	\hline
	\(42S(n-3) + 24 \) & 6744 & \cellcolor{yellow} 22536 & 70584 & 222036 \\
	\hline
	\(127S(n-4) + 68 \) & 5656 & 20388 & 68140 & 213428\\
	\hline
	\hline
	n & 12 & 13 & 14 & 15 \\
	\hline
	\(4S(n-1) + 2 \) & \cellcolor{yellow} 815314 & 2554194 & 8045162 & \cellcolor{yellow} 27061154\\
	\hline
	\(13S(n-2) + 8 \) & 792332 & \cellcolor{yellow}2649772 & 8301132 & 26146778 \\
	\hline
	\(42S(n-3) + 24 \) & 747750 & 2559840 & \cellcolor{yellow} 8560800 &  25886224 \\
	\hline
	\(127S(n-4) + 68 \) & 671390 & 2261049 & 7740464 & 25886224 \\
	\hline
\end{tabular}
\end{center}

With \( S(9) \geqslant 17803 \), we found a new lower bound for \(\WS(10)\) using Rowley's inequality.
Moreover, the third inequality gives new lower bounds for \(\WS(9)\) and \(WS(14)\).

>>>>

\section{Templates for weak Schur numbers}
\label{WeakSchur}

@@

\subsection{Inequality for weak Schur numbers using Schur and weak Schur numbers}

@@

\renewcommand{\arraystretch}{1.7}

\[
\begin{array}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
\cline{6-9}
   \multicolumn{5}{c|}{} & \cellcolor{green} 1 & \cellcolor{green} 2 & \cellcolor{blue} ... &\cellcolor{green} r & r + 1 & ... & b - 1 &  b \\
\hline
   \cellcolor{red} a - l & \cellcolor{red} a- l + 1 & \cellcolor{red} ... & \cellcolor{red} a - 1 & \cellcolor{red} a & \cellcolor{red} a + 1 & \cellcolor{red} ... &\cellcolor{red} a + r - 1 & \cellcolor{red} a + r & a + r + 1 & ... & a + b - 1 & a+ b \\
\hline
\cellcolor{yellow} 2 a - l &\cellcolor{yellow}...&\cellcolor{yellow}...&\cellcolor{yellow}...&\cellcolor{yellow} 2 a &\cellcolor{yellow} ... &\cellcolor{yellow} ... &\cellcolor{yellow} ... &\cellcolor{yellow} 2 a + r & ... & ... & ... & 2 a + b \\
\hline
...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
\hline
\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
\hline
p a - l & ... & ... & ... &p a & ... & ... & .... & p a + r & ... & ... & ... & p a + b\\
\hline
\end{array}
\]

\resetarraystretch

@@

\(\lambda\) is the function which maps an element \(x\) to its line number as mentioned in the intuitive explanation.

@@

\subsection{Inequalities and new lower bounds for Weak Schur numbers}

@@

\begin{center}
\begin{tabular}{|*{5}{c|}}
    \hline
	n & 8 & 9 & 10 & 11 \\
	\hline
	\(4S(n-1) + 2 \) & 6\,722 & 21\,146 & \cellcolor{yellow} 71\,214 & \cellcolor{yellow} 243\,794\\
	\hline
	\(13S(n-2) + 8 \) & \cellcolor{yellow} 6\,976 & 21\,848 & 68\,726 & 231\,447\\
	\hline
	\(42S(n-3) + 24 \) & 6\,744 & \cellcolor{yellow} 22\,536 & 70\,584 & 222\,036 \\
	\hline
	\(127S(n-4) + 68 \) & 5\,656 & 20\,388 & 68\,140 & 213\,428\\
	\hline
	\hline
	n & 12 & 13 & 14 & 15 \\
	\hline
	\(4S(n-1) + 2 \) & \cellcolor{yellow} 815\,314 & 2\,554\,194 & 8\,045\,162 & \cellcolor{yellow} 27\,061\,154\\
	\hline
	\(13S(n-2) + 8 \) & 792\,332 & \cellcolor{yellow}2\,649\,772 & 8\,301\,132 & 26\,146\,778 \\
	\hline
	\(42S(n-3) + 24 \) & 747\,750 & 2\,559\,840 & \cellcolor{yellow} 8\,560\,800 &  25\,886\,224 \\
	\hline
	\(127S(n-4) + 68 \) & 671\,390 & 2\,261\,049 & 7\,740\,464 & 25\,886\,224 \\
	\hline
\end{tabular}
\end{center}

With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using Rowley's inequality.
Moreover, the third inequality gives new lower bounds for \(\WS(9)\) and \(WS(14)\).
